---
title: "Coursework and Honors"
---
### Coursework

1. 2019 (IISc - Teaching Assistant)

```{r echo=FALSE, message=FALSE, warning=FALSE}
table1 <- tibble::tribble(
                           ~Course,           ~Facilitator,
             "Theoretical Ecology", "Dr. Vishwesha Guttal",
  "Advanced Ecological Statistics",   "Dr. Kavita Isvaran")

require(rhandsontable)
rhandsontable(table1, rowHeaders = NULL,
               digits = 3, useTypes = FALSE, search = FALSE,
               width = NULL, height = NULL)
```

2. 2018 (IISc - Audited)

```{r echo=FALSE, message=FALSE, warning=FALSE}
table2 <- tibble::tribble(
                 ~Course,                                  ~Facilitator,
  "Quantitative Ecology", "Dr. Kavita Isvaran and Dr. Vishwesha Guttal"
  )

require(rhandsontable)
rhandsontable(table2, rowHeaders = NULL,
               digits = 3, useTypes = FALSE, search = FALSE,
               width = NULL, height = NULL)

```

3. 2016 - 2018 (Pondicherry University - Coursework)

```{r echo=FALSE, message=FALSE, warning=FALSE}
table3 <- tibble::tribble(
                                              ~Course, ~Facilitator,
                               "Conservation Biology",          "A",
                             "Remote Sensing and GIS",         "A+",
                                          "Evolution",         "A-",
     "Environmental Informatics and Spatial Modeling",         "A+",
                                       "Biodiversity",         "A+",
                                      "Forest Botany",          "A",
                                     "Animal Ecology",          "A",
                                      "Plant Ecology",         "A+",
                        "Ecology of Medicinal Plants",         "A+",
                                        "Ornithology",          "A",
                                    "Aquatic Ecology",          "A",
                                "Terrestrial Ecology",         "A+",
                   "Population and Community Ecology",         "A+",
  "Statistics for Ecology and Environmental Sciences",         "A+"
  )

require(rhandsontable)
rhandsontable(table3, rowHeaders = NULL,
               digits = 3, useTypes = FALSE, search = FALSE,
               width = NULL, height = NULL)

```
### Honors

```{r echo=FALSE, message=FALSE, warning=FALSE}
table4 <- tibble::tribble(
                                 ~Award,                ~Organisation, ~Year,
  "Best Outgoing Student (Shortlisted)", "SSN College of Engineering",  2013,
                  "MENSA High IQ Award",                "MENSA India",  2012
  )

require(rhandsontable)
rhandsontable(table4, rowHeaders = NULL,
               digits = 3, useTypes = FALSE, search = FALSE,
               width = NULL, height = NULL)

```

### Competitive Examinations

1. Graduate Record Examination General Test GRE 2019 - *319.5 out of 346*
2. International English Language Testing System IELTS 2019 - *Band 8.5 out of 9*
3. Graduate Aptitude Test in Engineering GATE 2018 - Ecology and Evolution, *830 out of 1000*, All India Rank : 11
4. UGC-NET Environmental Sciences JRF & LS July 2018 Qualified
5. Test of English as a Foreign Language TOEFL 2012 - *111 out of 120*

### Scholarships

1. Merit scholarship semester 1 to 4 during M.Sc for scoring among the top 3 ranks.
2. University Rank 2 in M.Sc.
3. Merti scholarship year 1 during B.Tech for scoring among the top 3 ranks.
4. University Rank 38 out of 3870 candidates in B.Tech.